Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-04-19 PAPER/main.tex
changed notation and SCSPP definition

One prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004. A set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of heigh $H$ from left to right. Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places. A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:boxknife}). However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry). The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$. Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively. Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance. Specifically, as the items are packed from left to right, this involves checking the sum of the right-hand score width of each item $i$ and the left-hand score width of the next item $i+1$ on the strip. The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.

@@

\begin{definition}
	\label{defn:scspp}
	Given a set $\mathcal{I}$ of rectangular items of varying widths $w_i$ and score widths $a_i, b_i$ for each item $i \in \mathcal{I}$, a finite set of strips $S_j$ of equal fixed width $W$, and a minimum scoring distance $\tau$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance.
\end{definition}

@@

Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence in accordance with Theorem $\ref{thm:cpopsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the COP. Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$. $G'$ thus consists of a collection of alternating cycles $A_1, A_2, ..., A_{\lambda}$. If there is only one component on $G'$, i.e. $\lambda = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists. For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle. The algorithm thus executes a Bridge Recognition (BR) procedure that selects suitable edges in $R$ to be used as bridges between the components of $G'$, and will replace certain edges in $R'$.

@@

The sets $R_1, R_2, ..., R_k \subseteq R$ created during this process are then analysed. In the event that BR has been unable to produce a single set $R_1$, the components $A_1,..., A_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists. If there exists a set $R_i$ such that $|R_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':

@@

Else, if $k > 1$, it may be that multiple sets are required to combine the components of $G'$. Let $\mathcal{R}$ be a set that contains the sets $R_i$ needed to connect the components of $G'$ together, and let $\Lambda$ be a set that records the components covered by the sets in $\mathcal{R}$. Start by adding the components $A_i$ that each edge in $R_1$ is a member of to $\Lambda$, and then add $R_1$ to $\mathcal{R}$. At this stage, $|\Lambda| = |\mathcal{R}|$. Proceeding through the remaining sets $R_2, R_3, ..., R_k$, find a set $R_i$ that contains at least one edge that is a member of a component in $\Lambda$, and at least one edge that is a member of a component not yet recorded in $\Lambda$. Append the component that each edge in this set $R_i$ is a member of to $\Lambda$, provided the component is not already an element of $\Lambda$, then add $R_i$ to $\mathcal{R}$. Continue in this manner until the final set $R_k$ has been assessed. If $|\Lambda| = \lambda$, i.e. all components of $G'$ are elements of $\Lambda$, then the sets in $\mathcal{R}$ are able to combine the components of $G'$ to form a single alternating Hamiltonian cycle. This is achieved by repeating the connecting method described previously on every set $R_i \in \mathcal{R}$.

@@

\begin{equation}
	\label{eqn:lowerbound}
	k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{l}}
\end{equation}

>>>>

One prominent application of the COP is in a strip-packing problem brought to light as an open-combinatorial problem by \citeauthor{goulimis2004} in 2004. A set $\mathcal{I}$ of rectangular items of equal height $H$ made from cardboard are to be packed onto a strip of height $H$ from left to right. Each item $i \in \mathcal{I}$ has width $w_i \in \mathbb{Z}^{+}$, and possesses two vertical score lines, marked in predetermined places. A pair of knives mounted onto a bar cuts along the score lines of two adjacent items simultaneously, which allows the items to be folded with ease (see Figure \ref{fig:boxknife}). However, by design, the scoring knives cannot be placed too close to one another, and as such have a ``minimum scoring distance'' (around 70mm in industry). The distances between each score line and the nearest edge on an item $i \in \mathcal{I}$ are the score widths, $a_i, b_i \in \mathbb{Z}^{+}$, assigned such that $a_i \leq b_i$. Since these score widths are not necessarily equal, an item $i$ can be positioned in one of two orientations: ``regular'', denoted $(a_i, b_i)$, or ``rotated'', denoted $(b_i, a_i)$, where the smaller of the two score widths $a_i$ is on the left- and right- hand side of the item respectively. Clearly, for two items to be placed alongside one another feasibly, the sum of the adjacent score widths must equal or exceed the minimum scoring distance, else the knives will not be able to score the items in the correct locations. Thus, the problem consists of finding a suitable ordering and orientation of the items such that the sum of every pair of adjacent score widths is greater than or equal to the minimum scoring distance. Specifically, as the items are packed from left to right, this involves checking the sum of the right-hand score width of each item $i$ and the left-hand score width of the next item $i+1$ on the strip. The left-hand score width of the first item and the right-hand score width of the last item on the strip are not adjacent to any other item, and are therefore ignored.

@@

\begin{definition}
	\label{defn:scspp}
	Let $\mathcal{S} = S_1, S_2, ..., S_k$ be a set of strips of height $H$ and width $W$, and let $\mathcal{I}$ be a set of rectangular items of height $H$ and varying widths $w_i \in \mathbb{Z}^+ < W$ and score widths $a_i, b_i \in \mathbb{Z}^+$ such that $a_i \leq b_i$ and $a_i + b_i < w_i$ for each item $i \in \mathcal{I}$. Given a minimum scoring distance $\tau \in \mathbb{Z}^+$, the Score-Constrained Strip-Packing Problem (SCSPP) consists of finding the minimum number of strips $k$ required to pack all items in $\mathcal{I}$ such that the sum of every pair of adjacent score widths is greater than or equal to $\tau$.
\end{definition}

@@

Clearly, if $|R'| < n+1$, there are not enough matching edges to form an alternating Hamiltonian cycle along with the edges in $B$, and hence in accordance with Theorem $\ref{thm:cpopsoln}$ no feasible solution exists for the given instance $\mathcal{M}$ of the COP. Otherwise, if $R'$ is a perfect matching of cardinality $n+1$, the spanning subgraph $G'=(V, B \cup R')$ is a 2-regular graph, where each vertex is adjacent to its partner via an edge in $B$, and its match via an edge in $R'$. $G'$ thus consists of a collection of alternating cycles $C_1, C_2, ..., C_{\lambda}$. If there is only one component on $G'$, i.e. $\lambda = 1$, then this alternating cycle is in fact Hamiltonian, and therefore a feasible solution exists. For a graph $G'$ with $\lambda > 1$, the components of $G'$ must be combined to form one single alternating Hamiltonian cycle. The algorithm thus executes a Bridge Recognition (BR) procedure that selects suitable edges in $R$ to be used as bridges between the components of $G'$, and will replace certain edges in $R'$.

@@

The sets $R_1, R_2, ..., R_k \subseteq R$ created during this process are then analysed. In the event that BR has been unable to produce a single set $R_1$, the components $C_1,..., C_{\lambda}$ of $G'$ cannot be combined, and therefore no solution exists. If there exists a set $R_i$ such that $|R_i| = \lambda$, then all components on $G'$ can be combined using the following ``connecting method'':

@@

Else, if $k > 1$, it may be that multiple sets are required to combine the components of $G'$. Let $\mathcal{R}$ be a set that contains the sets $R_i$ needed to connect the components of $G'$ together, and let $\Lambda$ be a set that records the components covered by the sets in $\mathcal{R}$. Start by adding the components $C_i$ that each edge in $R_1$ is a member of to $\Lambda$, and then add $R_1$ to $\mathcal{R}$. At this stage, $|\Lambda| = |\mathcal{R}|$. Proceeding through the remaining sets $R_2, R_3, ..., R_k$, find a set $R_i$ that contains at least one edge that is a member of a component in $\Lambda$, and at least one edge that is a member of a component not yet recorded in $\Lambda$. Append the component that each edge in this set $R_i$ is a member of to $\Lambda$, provided the component is not already an element of $\Lambda$, then add $R_i$ to $\mathcal{R}$. Continue in this manner until the final set $R_k$ has been assessed. If $|\Lambda| = \lambda$, i.e. all components of $G'$ are elements of $\Lambda$, then the sets in $\mathcal{R}$ are able to combine the components of $G'$ to form a single alternating Hamiltonian cycle. This is achieved by repeating the connecting method described previously on every set $R_i \in \mathcal{R}$.

@@

\begin{equation}
	\label{eqn:lowerbound}
	k \geq \ceil*{\frac{\sum_{i=1}^{n}w_i}{W}}
\end{equation}
